---
title: "Final"
author: "Devin Maya"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
# some useful settings
knitr::opts_chunk$set(echo = TRUE, tidy.opts = list(width.cutoff = 55), tidy = TRUE, fig.align="center")
options(scipen=100)
options(tinytex.verbose = TRUE)
```

## Loading data

```{r}
# Load Haven package to load STATA file
library(haven)

# Create an indicator variable 
data<- read_dta("comp_ia_bootstrap3_RCT (5).dta")

# Viewing data
View(data)

head(data)
```

## Data cleaning & factoring & splicing

```{r}
#Creating new data frame for variables needed
v2 <- data$vote02
v8 <- data$vote98
v0 <- data$vote00
gen <- data$female
bus <- data$busy
nr <- data$newreg
con <- data$contact
re <- data$treat_real
age <- data$age

data_n <- data.frame(turnout = v2, vote02= v8, vote00= v0, gender = gen, busy = bus, n_reg_voter = nr, contact = con, treat = re, age = age)

data_n <- na.omit(data_n)
```

Variables we included in our new data frame:

vote02: Which is the outcome of interest- vote in 2002
treat_real: Assignment to treatment group
contact: Received phone call and responded to question "Can I count on you to vote next Tuesday?" regardless of answer
newreg - Newly registered voter
busy - Whether the phone line was busy when call was made
age - Age of the individual in years
female - Gender of the individual
vote00 - Voted in 2000 (prior to treatment)
vote98: Voted in 98 (prior to treatment

## Summary Statistics
```{r}
#Creating plot spaces
par(mfrow = c(1, 2))

#Getting summary statistics of treament
summary(data_n$treat)

#Getting plot for treatment variable
plot(factor(data_n$treat), xlab = "Conditions", ylab = "Participants Frequency", pch = 21, bg = 2, col = c(2,4))

legend("topright", fill = c(2, 4), legend = c("No Call",
"Call"), bty = "n")

#Getting summary statistics of output
summary(data_n$turnout)

#Getting plot for output variable
plot(factor(data_n$turnout),xlab = "Turnover", ylab = "Participants Frequency", pch = 21, bg = 2, col = c(3,5))

legend("topleft", fill = c(3, 5), legend = c("Did vote",
"No vote"), bty = "n")
```




## Running Regressions

### OLS
```{r}
#OLS just on treatment
OLS <- glm(turnout~ treat, data=data_n)
summary(OLS)

#OLS on treatment w/ controls
OLS_every <- glm(turnout~ ., data=data_n)
summary(OLS_every)
```

### Post-Lasso
```{r}
#Load Gamlr
library(gamlr)

#Creating Matrix
x<- model.matrix(turnout~(.+poly(age,2,raw=TRUE))^2 , data = data_n)[,-1]

#Checking dimensions of matrix
dim(x)
```

```{r}
#Post-LASSO

#Set seed
set.seed(0)

#Step 1
#LASSO regular for controls
y_mod <- cv.gamlr(x, data_n$turnout)

#Step 2
#LASSO on treatment
d_mod <- cv.gamlr(x,data_n$treat)

#Find non-zero coefficients
y_nonzero_coef <- which(coef(y_mod, select='min')[-1]!=0)
d_nonzero_coef <- which(coef(d_mod, select='min')[-1]!=0)

#Step 3
#Collect covariates
nz_coef_uni <- union(y_nonzero_coef, d_nonzero_coef)
#length(nz_coef_uni)

#Step 4
# Regress our outcome Y on D and W
# Y = Voter Turnout rate
# D = Randomization of getting a phone call or not
# W = Controls

#Creating new data frame that we'll use for POST-LASSO
pl_data <- data.frame(voter_turnout_rate =data_n$turnout, treatment = data_n$treat, as.matrix(x[,nz_coef_uni]))


#Final step (POSTLASSO)
post_lasso <- glm(voter_turnout_rate~., data = pl_data)
coef(summary(post_lasso))

#Finding the treatment
coef(summary(post_lasso))["treatment", ]
```

## Counter Factual

Assume every Participants get called
```{r}
#Counter factual situation, where treatment is true

#Creating c_fact
#Copying old data frame used for Post-Lasso, and making treatments=1
treat_cf <- pl_data
treat_cf$treatment <- 1

#Average of counterfactual
a <-mean(predict(post_lasso, treat_cf))
a

#Average of dataset
b <- mean(pl_data$voter_turnout_rate)
b

#Difference btwn both averages
a-b
```
```


